Detecting Facial Expressions in Professional Tennis Matches

### 2017-09-01 Report06-12.Rmd
New regression model table

ModelPlotResults<-function(model, data = GlmModelEstimates(model)){
  ep<-EstimatesPlot(model, data)
  #sp<- SignificancePlot(model, data) 
  grid.arrange(ep)#, sp)
}

@@

```{r CheckModels}

mods<-GlmModelCreation(model = hit ~ 0 + 
              shotangle + 
              bg + 
              bg*shotangle + 
              situation + 
              obscured +
              headangle +
              lighting + 
              glasses + 
              visorhat, 
              data=ALLmetaIMGnamedFaces)

#mods$Animetrics %>% drop1(., test="Chisq")
#mods$Google %>% drop1(., test="Chisq")
#interaction significant
#mods$Microsoft %>% drop1(., test="Chisq")
#mods$Skybiometry %>% drop1(., test="Chisq")

# mods$Animetrics %>% 
#   summary %>%
#   .$coefficients %>%
#   as.data.frame() %>% select(Estimate, `Pr(>|z|)`) -> a

The model selection technique was undertaking a Chi-Square test comparing the model deviance with all variables to the model deviance when each particular variable was excluded. If there was a low Pr(>Chi) value associated with a variable, that would show the variable was significant in predicting whether the faces annotated manually would be detected by the API.

```{r Regression, fig.width=7.5, fig.cap = "The figure depicts the change in the probability of a face being detected by the APIs given a certain attribute level associated with the face. Wearing either glasses, or headwear, a visor or a hat, significantly decreased the likelihood of a manually annotated face being detected by the APIs.\\label{fig:Regression}"}

ModelPlotResults(hit ~ shotangle + bg + bg*shotangle + situation + lighting + glasses + visorhat)

```{r GoogleRegression, fig.cap = "Google Regression\\label{fig:GoogleRegression}"}
ALLmetaIMGnamedFaces %>% filter(type=="Manual" | type=="Google") %>%
  mutate(isplayer = ifelse(detect=="Player", 1, 0)) -> players

>>>>

ModelPlotResults<-function(model, data = GlmModelEstimates(model)){
  ep<-EstimatesPlot(model, data)
  #sp<- SignificancePlot(model, data) 
  grid.arrange(ep)#, sp)
}
```

```{r ModelEstimates, fig.cap ="\\label{tab:Image-Characteristics-Table}"}
GlmModelEstimates(model = hit ~ 0 + 
              shotangle + 
              bg + 
              bg*shotangle + 
              situation + 
              obscured +
              headangle +
              lighting + 
              glasses + 
              visorhat) -> ModelEstimates
#Create estimates columns
ModelEstimates %>% mutate(Estimate = round(Estimate,2)) %>%
select(variable, type, Estimate) %>%
  spread(key=type, value=Estimate) %>%
  select(variable, A.e=Animetrics, G.e=Google, M.e=Microsoft, S.e=Skybiometry)-> ModelEstimatesTypes

#Create significance columns
ModelEstimates %>% mutate(sig = ifelse(`Pr(>|z|)` <= 0, "***", 
                            ifelse(`Pr(>|z|)` <= 0.001, "** ",
                            ifelse(`Pr(>|z|)` <= 0.010, "*  ",
                            ifelse(`Pr(>|z|)` <= 0.050, ".  ", 
                                                        "   ")))))  %>%
select(variable, type, sig) %>% 
  spread(key=type, value=sig) %>% 
  select(variable, A.s=Animetrics, G.s=Google, M.s=Microsoft, S.s=Skybiometry) -> ModelEstimatesSign

ModelEstimatesTable <- as.data.frame(cbind(ModelEstimatesTypes, ModelEstimatesSign[,2:5])) %>% 
  unite(Animetrics, A.e, A.s, sep="") %>% 
  unite(Google, G.e, G.s, sep="") %>% 
  unite(Microsoft, M.e, M.s, sep="") %>% 
  unite(Skybiometry, S.e, S.s, sep="")

knitr::kable(ModelEstimatesTable, align=c("l", "r", "r", "r", "r"),
             booktabs = TRUE, longtable=TRUE, caption="", format = "latex")
```

The variables were kept if they were significant.

```{r Regression, fig.width=7.5, fig.cap = "The figure depicts the change in the probability of a face being detected by the APIs given a certain attribute level associated with the face. Wearing either glasses, or headwear, a visor or a hat, significantly decreased the likelihood of a manually annotated face being detected by the APIs.\\label{fig:Regression}", eval=FALSE}

#unnecessary as table is included
#ModelPlotResults(hit ~ shotangle + bg + bg*shotangle + situation + lighting + glasses + visorhat)

@@

```{r GoogleRegression, fig.cap = "Google Regression\\label{fig:GoogleRegression}"}
aminFaces %>% filter(type=="Manual" | type=="Google") %>%
  mutate(isplayer = ifelse(detect=="Player", 1, 0)) -> players
